General Physics Formula

### 2016-10-20 GRE Physics Prep/General Physics Formula.tex
New GRE physics prepare.

@@

\paragraph{Oscillation} (\textbf{pp.403 of \cite{book}})
\begin{align}
    \omega &= \frac{2\pi}{T} = 2\pi f
\end{align}
\textbf{Linear Oscillator}
\begin{align}
    & \omega = \sqrt{\frac{k}{m}} \\
    & T = 2\pi \sqrt{\frac{m}{k}} 
\end{align}
\textbf{Pendulums}
\begin{align}
    & T = 2\pi \sqrt{I/\kappa} \\
    & T = 2\pi \sqrt{L/g} \\
    & T = 2\pi \sqrt{I/mgh}
\end{align}
\textbf{Damped Harmonic Motion}
\begin{align}
    & x(t) = x_m e^{-bt/2m} \cos\left( \omega' t+\phi\right) \\
    & \omega' = \sqrt{ \frac{k}{m} - \frac{b^2}{4m^2} } \\
    & E(t)\approx \frac{1}{2} kx_m^2 e^{-bt/m}
\end{align}
\paragraph{Waves} (\textbf{pp.436 ch16 of \cite{book}})
\begin{align}
    & y(x,t) = y_m \sin(kx-\omega t) \\
    & k = \frac{2\pi}{\lambda} \\
    & f = \frac{\omega}{2\pi} = \frac{1}{T} \\
    & v = \frac{\omega}{k} = \frac{\lambda}{T} = \lambda f
\end{align}
\textbf{String}
\begin{align}
    & v = \frac{\tau}{\mu} \\
    & P_\text{avg} = \frac{1}{2}\mu v \omega^2 y_m^2
\end{align}
\textbf{Resonance}
\begin{align}
    n \lambda = 2L
\end{align}
\paragraph{Longitudinal Wave} (\textbf{pp.466 ch17 of \cite{book}})
\begin{align}
    & v = \sqrt{\frac{B}{\rho}} \\
    & s = s_m \cos(kx-\omega t) \\
    & \Delta p = \Delta p_m sin(kx-\omega r) \\
    & \Delta p_m = (v\rho \omega) s_m
\end{align}
\textbf{Sound Intensity}
\begin{align}
    & I = \frac{P}{A} \\
    & I = \frac{1}{2}\rho v \omega^2 s_m^2 \\
    & I = \frac{P_s}{4\pi r^2} \\
\end{align}
\textbf{Standing Wave Patterns in Pipes}
\begin{align}
    & f = \frac{v}{\lambda} = \frac{nv}{2L}\text{, $n=1,2,3,\cdots$} \\
    & f = \frac{v}{\lambda} = \frac{nv}{4L}\text{, $n=1,3,5,\cdots$}
\end{align}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch17.sound_wave}.png}
\end{figure}
\textbf{Beat}
\begin{align}
    f_\text{beat} = f_1 - f_2
\end{align}
\textbf{The Doppler Effect}
\begin{align}
    f' = f \frac{ v \pm v_D}{ v\pm v_s}
\end{align}
The signs are chosen such that $f'$ tends to be \textit{greater} for
motion toward and \textit{less} for motion away.
\textbf{Shock wave}
\begin{align}
    \sin{\theta} = \frac{v}{v_s}\text{ , $v_s\geq v$}
\end{align}

@@

@@

\begin{align}
    \mathcal{E} = \int \vec{E} \diff \vec{s} \\
\end{align}
\textbf{Inductance}
\begin{align}
    & L \equiv \frac{N\Phi_B}{i} \\
    & \frac{L}{l} = \mu_n n^2 A \\
    & \mathcal{E}_L = - L\frac{\diff i}{\diff t} \\
    & U_B = \frac{1}{2} L i^2 \\
    & u_B = \frac{1}{2} \frac{B^2}{\mu_0} 
\end{align}
\section{Anchor}
\label{sec:anchor}
\begin{thebibliography}{1}
    \bibitem{book} Fundamentals of Physics, Extended Edition. Halliday
    \& Resnick.
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

\section{Fluid}
\label{sec:Fluid}

@@

\section{Wave}
\label{sec:Wave}

\paragraph{Oscillation} (\textbf{pp.403 of \cite{book}})
\begin{align}
    \omega &= \frac{2\pi}{T} = 2\pi f
\end{align}
\textbf{Linear Oscillator}
\begin{align}
    & \omega = \sqrt{\frac{k}{m}} \\
    & T = 2\pi \sqrt{\frac{m}{k}} 
\end{align}
\textbf{Pendulums}
\begin{align}
    & T = 2\pi \sqrt{I/\kappa} \\
    & T = 2\pi \sqrt{L/g} \\
    & T = 2\pi \sqrt{I/mgh}
\end{align}
\textbf{Damped Harmonic Motion}
\begin{align}
    & x(t) = x_m e^{-bt/2m} \cos\left( \omega' t+\phi\right) \\
    & \omega' = \sqrt{ \frac{k}{m} - \frac{b^2}{4m^2} } \\
    & E(t)\approx \frac{1}{2} kx_m^2 e^{-bt/m}
\end{align}

\paragraph{Waves} (\textbf{pp.436 ch16 of \cite{book}})
\begin{align}
    & y(x,t) = y_m \sin(kx-\omega t) \\
    & k = \frac{2\pi}{\lambda} \\
    & f = \frac{\omega}{2\pi} = \frac{1}{T} \\
    & v = \frac{\omega}{k} = \frac{\lambda}{T} = \lambda f
\end{align}
\textbf{String}
\begin{align}
    & v = \frac{\tau}{\mu} \\
    & P_\text{avg} = \frac{1}{2}\mu v \omega^2 y_m^2
\end{align}
\textbf{Resonance}
\begin{align}
    n \lambda = 2L
\end{align}
\paragraph{Longitudinal Wave} (\textbf{pp.466 ch17 of \cite{book}})
\begin{align}
    & v = \sqrt{\frac{B}{\rho}} \\
    & s = s_m \cos(kx-\omega t) \\
    & \Delta p = \Delta p_m sin(kx-\omega r) \\
    & \Delta p_m = (v\rho \omega) s_m
\end{align}
\textbf{Sound Intensity}
\begin{align}
    & I = \frac{P}{A} \\
    & I = \frac{1}{2}\rho v \omega^2 s_m^2 \\
    & I = \frac{P_s}{4\pi r^2} \\
\end{align}
\textbf{Standing Wave Patterns in Pipes}
\begin{align}
    & f = \frac{v}{\lambda} = \frac{nv}{2L}\text{, $n=1,2,3,\cdots$} \\
    & f = \frac{v}{\lambda} = \frac{nv}{4L}\text{, $n=1,3,5,\cdots$}
\end{align}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch17.sound_wave}.png}
\end{figure}
\textbf{Beat}
\begin{align}
    f_\text{beat} = f_1 - f_2
\end{align}
\textbf{The Doppler Effect}
\begin{align}
    f' = f \frac{ v \pm v_D}{ v\pm v_s}
\end{align}
The signs are chosen such that $f'$ tends to be \textit{greater} for
motion toward and \textit{less} for motion away.
\textbf{Shock wave}
\begin{align}
    \sin{\theta} = \frac{v}{v_s}\text{ , $v_s\geq v$}
\end{align}

\section{Thermal Physics}
\label{sec:Thermal-Physics}

@@

\section{Electrodynamics}
\label{sec:Electrodynamics}

@@

\begin{align}
    \mathcal{E} = \oint \vec{E} \diff \vec{s} \\
\end{align}
\textbf{Inductance}
\begin{align}
    & L \equiv \frac{N\Phi_B}{i} \\
    & \frac{L}{l} = \mu_n n^2 A \\
    & \mathcal{E}_L = - L\frac{\diff i}{\diff t} \\
    & U_B = \frac{1}{2} L i^2 \\
    & u_B = \frac{1}{2} \frac{B^2}{\mu_0} 
\end{align}

\paragraph{LC Circuit} (\textbf{pp.853 ch31 of \cite{book}})

\begin{align}
    & U_E = \frac{q^2}{2C} \\
    & U_B = \frac{L i^2}{2} \\
    & \omega = \frac{1}{\sqrt{LC}}
\end{align}
Predicting RLC current (\textbf{pp.843 of \cite{book}})

\paragraph{Maxwell's Equations} (\textbf{pp.869 of \cite{book}})

\begin{align}
    & \oint \vec{E} \cdot \diff \vec{A} = q_\text{enc}/\varepsilon_0
    \\
    & \oint \vec{B} \cdot\diff\vec{A} = 0 \\
    & \oint \vec{E}\cdot\diff\vec{s} = -\frac{\diff\Phi_B}{\diff t} \\
    & \oint \vec{B}\cdot\diff\vec{s} = 
    \mu_0\varepsilon_0 \frac{\diff\Phi_E}{\diff t} +\mu_0 i_\text{enc}
    \nonumber\\
    & \,= \mu_0 i_d + \mu_0 i_\text{enc}
\end{align}

(\textbf{pp.882 ch32 of \cite{book}})

\textbf{Spin}
\begin{align}
    & \mu_s = -\frac{e}{m} S \\
    & \mu_B = \frac{e\hbar}{2m} = 9.27\times 10^{-24} \text{J/T} \\
    & \mu_\text{orb} = -\frac{e}{2m} L_\text{orb}
\end{align}
\textbf{Curie's law} 
\begin{align}
    M = C\frac{B_\text{ext}}{T}
\end{align}

\paragraph{Optics} (\textbf{pp.913 ch33 of \cite{book}})
\begin{align}
    & \vec{S} = \frac{1}{\mu_0} \vec{E}\times\vec{B} \\
    & F = \frac{IA}{c} \text{ (total absorption)} \\
    & F = \frac{2IA}{c} \text{ (total reflection)} \\
    & I = I_0 \cos^2{\theta} \\
    & n_1 \sin{\theta_1} = n_2 \sin{\theta_2} \\
    & \theta_c = \sin^{-1}\frac{n_2}{n_1} \\
    & \theta_B = \tan^{-1}\frac{n_2}{n_1}
\end{align}

\paragraph{Optics 2} (\textbf{pp.948 ch34 of \cite{book}})
\begin{align}
    \text{Omitted}
\end{align}

\paragraph{Interference} (\textbf{pp.981 ch35 of \cite{book}})

\begin{align}
    & \lambda_n = \frac{\lambda}{n} \\
    & 2L = (m+\frac{1}{2})\frac{\lambda}{n_2} \text{ (thin film, max)}
    \\
    & d\sin{\theta} = m\lambda \text{ (Young's, max)}
\end{align}

\paragraph{Diffraction} (\textbf{pp.1013 ch36 of \cite{book}})

\begin{align}
    a\sin{\theta} &= m \lambda \text{, $m=1,2,\cdots$ (single-slit
    minima)} \\
    \theta_R &= 1.22\frac{\lambda}{d} \text{ (Rayleigh's criterion)}
    \\
    I(\theta) &=  I_m
      (\cos^2\beta)\left(\frac{\sin{\alpha}}{\alpha}\right)^2 \\
    \beta &= (\pi d/\lambda),\, \alpha = (\pi a/\lambda)\sin\theta \\
    d\sin{\theta} &= m\lambda \text{, $m=0,1,2\cdots$ (diffraction
      grating maxima)} \\
    2d\sin{\theta} &= m\lambda \text{, $m=1,2,\cdots$ (Bragg's law)}
\end{align}

\paragraph{Relativity} (\textbf{pp.1048 ch37 of \cite{book}})
\begin{align}
    \Delta t &= \gamma \Delta t_0 \\
    L &= L_0/\gamma \\
    x' &= \gamma(x-vt) \\
    t' &= \gamma(t-vx/c^2) \\
    u &= \frac{u'+v}{1+u'v/c^2} \\
    f &= f_0 \sqrt{\frac{1-\beta}{1+\beta}} \\
    f &= f_0 \sqrt{1-\beta^2} \\
    \vec{p} &= \gamma m \vec{v} \\
    E &= mc^2 + K = \gamma mc^2 \\
    E^2 &= (pc)^2 + (mc^2)^r
\end{align}

\paragraph{Photon} (\textbf{pp.1077 ch38 of \cite{book}})
\begin{align}
    & E = h f \\
    & p= \frac{hf}{c} = \frac{h}{\lambda} \\
    & hf = K_\text{max} + \Phi_\text{work function} \\
    & \Delta\lambda = \frac{h}{mc}(1-\cos{\phi})
\end{align}

\paragraph{Conductions} (\textbf{pp.1160 ch41 of \cite{book}})
\begin{align}
    P(E) &= \frac{1}{e^{(E-E_F)/kT} +1} 
\end{align}

\section{Anchor}
\label{sec:anchor}
\begin{thebibliography}{1}
    \bibitem{book} Fundamentals of Physics, Extended Edition. Halliday
    \& Resnick.
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}
